### 2016-12-31 README.Rmd

A version of this vignette is also available through CRAN [here](https://cran.r-project.org/web/packages/futureheatwaves/vignettes/futureheatwaves.html).

>>>>

A version of this vignette is also available through CRAN [here](https://CRAN.R-project.org/package=futureheatwaves/vignettes/futureheatwaves.html).
